% Copyright 2013 Christophe-Marie Duquesne <chmd@chmd.fr>
% Copyright 2014 Mark Szepieniec <http://github.com/mszep>
% 
% ConText style for making a resume with pandoc. Inspired by moderncv.
% 
% This CSS document is delivered to you under the CC BY-SA 3.0 License.
% https://creativecommons.org/licenses/by-sa/3.0/deed.en_US

\startmode[*mkii]
  \enableregime[utf-8]  
  \setupcolors[state=start]
\stopmode

\setupcolor[hex]
\definecolor[titlegrey][h=757575]
\definecolor[sectioncolor][h=397249]
\definecolor[rulecolor][h=9cb770]

% Enable hyperlinks
\setupinteraction[state=start, color=sectioncolor]

\setuppapersize [A4][A4]
\setuplayout    [width=middle, height=middle,
                 backspace=20mm, cutspace=0mm,
                 topspace=10mm, bottomspace=20mm,
                 header=0mm, footer=0mm]

%\setuppagenumbering[location={footer,center}]

\setupbodyfont[11pt, helvetica]

\setupwhitespace[medium]

\setupblackrules[width=31mm, color=rulecolor]

\setuphead[chapter]      [style=\tfd]
\setuphead[section]      [style=\tfd\bf, color=titlegrey, align=middle]
\setuphead[subsection]   [style=\tfb\bf, color=sectioncolor, align=right,
                          before={\leavevmode\blackrule\hspace}]
\setuphead[subsubsection][style=\bf]

\setuphead[chapter, section, subsection, subsubsection][number=no]

%\setupdescriptions[width=10mm]

\definedescription
  [description]
  [headstyle=bold, style=normal,
   location=hanging, width=18mm, distance=14mm, margin=0cm]

\setupitemize[autointro, packed]    % prevent orphan list intro
\setupitemize[indentnext=no]

\setupfloat[figure][default={here,nonumber}]
\setupfloat[table][default={here,nonumber}]

\setuptables[textwidth=max, HL=none]

\setupthinrules[width=15em] % width of horizontal rules

\setupdelimitedtext
  [blockquote]
  [before={\setupalign[middle]},
   indentnext=no,
  ]


\starttext

\section[chinmay-pandhare]{Chinmay Pandhare}

\subsection[contact-me]{Contact Me}

\placetable[none]{}
\starttable[|c|c|]
\HL
\NC Platform
\NC Contact
\NC\AR
\HL
\NC Email
\NC \useURL[url1][mailto:ccpandhare@gmail.com][][ccpandhare@gmail.com]\from[url1]
\NC\AR
\NC LinkedIn
\NC \useURL[url2][https://linkedin.com/in/ccpandhare][][ccpandhare]\from[url2]
\NC\AR
\NC WhatsApp
\NC \useURL[url3][tel:+917718823969][][+91 7718823969]\from[url3]
\NC\AR
\NC Phone
\NC \useURL[url4][tel:+919829533001][][+91 9829533001]\from[url4]
\NC\AR
\HL
\stoptable

\subsection[education]{Education}

Birla Institute of Technology and Science, Pilani -- Pilani Campus

B.E. Electrical and Electronics Engineering (Current student)

Year of Graduation : 2020

\subsection[bio]{Bio}

I am a developer and develop in many languages including, but not
limited to \type{JavaScript}, \type{Node.js}, \type{Python},
\type{C/C++}. Most of my experience is in Web Development. I pick up new
technologies with ease.

\subsection[experience]{Experience}

\subsubsubsection[google-summer-of-code-2017-june-2017---present]{Google
Summer of Code 2017 (June 2017 - Present)}

I am currently a GSoC student for the organization
\useURL[url5][https://publiclab.org][][PublicLab]\from[url5]. My project
is to create a system for image manipulation. The repository for the
same can be found
\useURL[url6][https://github.com/publiclab/image-sequencer][][here]\from[url6].
The project is in \type{Node.js}.

\subsubsubsection[jhunjhunu-district-court-january-2017---present]{Jhunjhunu
District Court (January 2017 - Present)}

I am working on a project for the District Court of Jhunjhunu,
Rajasthan. This project aims at reducing corruption and the digitization
of file copying system. It involves creating a WebApp. Upon success, the
project will be replicated across the state of Rajasthan. The project's
backend is written in \type{PHP}.

\subsection[team-work]{Team Work}

\subsubsubsection[dvm-bits-pilani-august-2016---present]{DVM BITS Pilani
(August 2016 - Present)}

I am a front-end developer at the Department of Visual Media (DVM) in
BITS Pilani. It is responsible for developing Websites, Mobile
Applications, Registration Software and Trailers, Teasers, Videos of the
fests at BITS Pilani. My major contributions have been to the
\useURL[url7][https://bits-bosm.org/2017/][][BOSM Intro
Website]\from[url7].
\useURL[url8][https://github.com/dvm-bitspilani][][This]\from[url8] is
the link to the Department GitHub organization.

\subsubsubsection[nss-bits-pilani-march-2017---present]{NSS, BITS Pilani
(March 2017 - Present)}

I am a Web Developer for the National Service Scheme, BITS Pilani
Chapter.

\subsubsubsection[cel-bits-pilani-august-2016---december-2016]{CEL, BITS
Pilani (August 2016 - December 2016)}

For a short period of time, i was a member of the Centre for
Entrepreneurial leadership n BITS Pilani.

\stoptext
